\chapter{More on local structure}

This chapter serves for the second half of the commutative algebra preparation of the remaining part of the paper. The key result is
\begin{enumerate}
  \item \Cref{thm:weakly-etale-ind-etale} expressing that every weakly etale map can be covered by ind-etale maps.
\end{enumerate}
The proof goes via the local input \label{weakly-etale-over-sh}.

\begin{lemma}[{\cite[\href{https://stacks.math.columbia.edu/tag/04GH}{Tag 04GH, (1)}]{stacks-project}}]
    Let $R$ be a Henselian local ring and $S$ a finite $R$-algebra. Then $S$ is
    a finite product of Henselian local rings, each finite over $R$.
    \label{lemma:finite-over-henselian-local}
\end{lemma}

\begin{proof}
    Omitted, will be in mathlib soon.
\end{proof}

\begin{lemma}
    A filtered colimit of local rings along local homomorphisms is local.
    \label{lemma:colimit-local}
\end{lemma}

\begin{proof}
    Let $R = \colim_i R_i$ with $R_i$ local rings and $R_i \to R_j$ a local ring map.
    Suppose $x, y \in R_i$ are non-units. Since $R_i$ is local, their sum is a not a unit.
    If the image of $x + y$ in $\colim_i R_i$ is a unit, their exists a $j$ such that the image of $x + y$ is a
    unit in $R_j$. But this does not happen because $R_i \to R_j$ is a local ring map.
\end{proof}

\begin{lemma}[{\cite[\href{https://stacks.math.columbia.edu/tag/04GI}{Tag 04GI}]{stacks-project}}]
    A filtered colimit of (strictly) Henselian local rings along local homomorphisms is
    (strictly) Henselian.
    \label{lemma:colimit-henselian-local}
\end{lemma}

\begin{proof}
    % Not needed at the moment.
    Omitted.
\end{proof}

\begin{lemma}
    Let $R$ be a Henselian local ring and $S$ be an integral $R$-algebra and an integral domain.
    Then $S$ is a local ring.
    \label{lemma:henselian-local-integral-local}
\end{lemma}

\begin{proof}
    \uses{lemma:colimit-local, lemma:finite-over-henselian-local}
    Since $S$ is integral over $R$, it is the colimit of its finite $R$-sub-algebras. Since
    a subring of an integral domain is still an integral domain, by \Cref{lemma:colimit-local} we
    may assume that $S$ is finite over $R$.
    By \Cref{lemma:finite-over-henselian-local}, $S$ is a product of (Henselian) local rings and hence
    local as an integral domain.
\end{proof}

\begin{lemma}
    Let $R \to S$ be an integral ring map of local rings. Then $R \to S$ is a local ring homomorphism.
    \label{lemma:integral-local-hom}
\end{lemma}

\begin{proof}
    This follows from going-up (use \verb`Ideal.IsMaximal.under`).
\end{proof}

\begin{lemma}
    Let $R \to S$ be a local ring homomorphism of local rings. If $R \to S$ is integral,
    the extension of residue fields $\kappa(S) / \kappa(R)$ is algebraic.
    \label{lemma:integral-local-algebraic-residue-field}
\end{lemma}

\begin{proof}
    It suffices to show that $\kappa(S)$ is integral over $R$. Since $S$ is integral over $R$
    and $\kappa(S)$ is integral over $S$ (the map $S \to \kappa(S)$ is surjective),
    the composition $R \to S \to \kappa(S)$ is integral.
\end{proof}

\begin{lemma}[{\cite[\href{https://stacks.math.columbia.edu/tag/092Y}{Tag 092Y}]{stacks-project}}]
    Let $R \to S$ and $R \to T$ be local ring maps of local rings. Suppose
    $R \to S$ is integral and $\kappa(S) / \kappa(R)$ or $\kappa(T) / \kappa(S)$
    is purely inseparable, then $T \otimes_{R} S$ is a local ring.
    \label{lemma:tensorprod-local-purely-inseparable}
\end{lemma}

\begin{proof}
    Integral is stable under base change, so $T \to S' = T \otimes_{R} S$ is integral. Hence by going-up
    any maximal ideal of $S'$ lies over $\mathfrak{m}_T$. We have
    \[
        S' / \mathfrak{m}_T S' = \kappa(T) \otimes_{R} S = \kappa(T) \otimes_{\kappa(R)} S / \mathfrak{m}_R S
    .\] Again by going-up and since $S$ is local, $\spec{S / \mathfrak{m}_R S}$ is
    a single point. Thus $\spec{S' / \mathfrak{m}_T S'} \cong \spec{\kappa(T) \otimes_{\kappa(R)} \kappa(S)}$.
    The latter is a single point, because purely inseparable extensions induce
    universal homeomorphisms.
\end{proof}

\section{Weakly étale algebras}

Ind-étale is a practical notion, since it usually allows reducing proofs to the étale case. Geometrically,
ind-étale is badly behaved though, since it is not local on the (geometric) target. For this reason, when we later
define the pro-étale site of a scheme, we use the notion of weakly étale ring maps instead.

\begin{definition}[Weakly étale algebras]
    An $R$-algebra $S$ is \emph{weakly étale} if it is flat over $R$ and flat over $S \otimes_{R} S$.
    A ring homorphism $f \colon R \to S$ is \emph{weakly étale} if $S$ is weakly étale as an $R$-algebra.
    \label{def:weakly-etale-algebra}
    \lean{Algebra.WeaklyEtale}
    \leanok
\end{definition}

Historically, the property weakly étale is studied under the name of \emph{absolutely flat}. 
\Cref{lemma:weakly-etale-flat} partially justifies this name. Furthermore, we have an absolute version 
of this property.

\begin{definition}
    \label{def:absolutely-flat}
    A ring $A$ is called \emph{absolutely flat} if every $A$-module is flat over $A$. 
    \lean{Ring.AbsolutelyFlat, Ring.AbsolutelyFlat.instFlat}
\end{definition}

\begin{lemma}
    Every étale algebra is weakly étale.
    \label{lemma:etale-weakly-etale-algebra}
    \lean{Algebra.WeaklyEtale.of_etale}
    \uses{def:weakly-etale-algebra}
\end{lemma}

\begin{proof}
    \leanok
    Let $S$ be an étale $R$-algebra. Then $S$ is $R$-flat. Also
    $S \otimes_{R} S \cong S × T$ for some ring $T$, in particular $\spec{S \otimes_{R} S} \to \spec{S}$ is
    an open immersion, hence flat.
\end{proof}

\begin{lemma}
    \label{lem:field-absolutely-flat}
    A field is absolutely flat.
    \uses{def:absolutely-flat}
\end{lemma}

\begin{proof}
    Omitted.
\end{proof}

\begin{lemma}[\stacksproject{092J}]
    \lemma{lem:weakly-etale-comp}
    If $A \to B$ and $B \to C$ are weakly étale, then $A \to C$ is weakly étale.
\end{lemma}

\begin{proof}
    Ommited, see \stacksproject{092J}.
\end{proof}

\begin{lemma}[\stacksproject{092H}]
    \label{lem:weakly-etale-base-change}
    If $B$ is a weakly-étale $A$-algebra and $A'$ is any $A$-algebra, the base change
    $A' \otimes_{A} B$ is a weakly-étale $A'$-algebra.
    \uses{def:weakly-etale-algebra}
    \lean{Algebra.WeaklyEtale.tensorProduct}
    \leanok
\end{lemma}

\begin{proof}
    Calculation, see \stacksproject{092H}.
    \leanok
\end{proof}

\begin{lemma}[\stacksproject{092C}]
    Let $B$ be an $A$-algebra such that $B \otimes_{A} B \to B$ is flat. Let $N$ be a $B$-module.
    If $N$ is flat as a $A$-module, then $N$ is flat as a $B$-module.
    \label{lemma:weakly-etale-flat}
    \lean{Module.Flat.of_flat_lmul'_of_flat}
    \leanok
\end{lemma}

\begin{proof}
    \leanok 
    % Note: the formal proof actually goes through element chasing, see the commented proof below.
    If $N'$ is a second $B$-module, then
    \[
        N \otimes_B N' = B \otimes_{B \otimes_{A} B} (N \otimes_{A} N')
    .\]
    Hence this follows from the definitions.
\end{proof}

% Note: Another proof by Gemmini using element chasing

% \begin{theorem}
% Let $A$ be a commutative ring, and let $B$ be an $A$-algebra such that the multiplication map $\mu: B \otimes_A B \to B$ is flat. Let $M$ be a $B$-module. If $M$ is flat as an $A$-module, then $M$ is flat as a $B$-module.
% \end{theorem}

% \begin{proof}
% To prove that $M$ is flat as a $B$-module, we will use the equational criterion for flatness: we must show that for any finite relation $\sum_{i=1}^n b_i m_i = 0$ in $M$ (where $b_i \in B$ and $m_i \in M$), there exist elements $m'_s \in M$ and $d_{is} \in B$ such that $m_i = \sum_{s=1}^S d_{is} m'_s$ for all $i$, and $\sum_{i=1}^n b_i d_{is} = 0$ for all $s$.

% \medskip\noindent
% \textbf{Step 1: The flat epimorphism property.} \\
% Let $I = \ker(\mu)$. Since $B$ is a flat $B \otimes_A B$-module, $I$ is a pure ideal. Consider the elements $z_i = 1 \otimes b_i - b_i \otimes 1 \in B \otimes_A B$. Clearly, $\mu(z_i) = b_i - b_i = 0$, so $z_i \in I$ for all $i = 1, \dots, n$. 

% By the pureness of $I$, there exists an element $t = \sum_{k=1}^K u_k \otimes v_k \in B \otimes_A B$ such that $\mu(t) = 1$ and $t z_i = 0$ for all $i$. 
% The condition $\mu(t) = 1$ means $\sum_{k=1}^K u_k v_k = 1$. 
% The condition $t z_i = 0$ implies $t(1 \otimes b_i) = t(b_i \otimes 1)$, which expands to:
% \begin{equation} \label{eq:bump}
% \sum_{k=1}^K u_k \otimes v_k b_i = \sum_{k=1}^K b_i u_k \otimes v_k \quad \text{in } B \otimes_A B.
% \end{equation}

% \medskip\noindent
% \textbf{Step 2: Constructing a relation in $B \otimes_A M$.} \\
% Define the elements $y_i \in B \otimes_A M$ for $i = 1, \dots, n$ by:
% \[
% y_i = \sum_{k=1}^K u_k \otimes (v_k m_i).
% \]
% Let us evaluate the sum $\sum_{i=1}^n b_i y_i$ in the $B$-module $B \otimes_A M$ (where $B$ acts on the left factor):
% \[
% \sum_{i=1}^n b_i y_i = \sum_{i=1}^n \sum_{k=1}^K (b_i u_k) \otimes (v_k m_i).
% \]
% Because the map $x \otimes y \mapsto x \otimes ym_i$ from $B \otimes_A B \to B \otimes_A M$ is a well-defined $A$-linear homomorphism, we can apply it to equation (\ref{eq:bump}) to shift the $b_i$ factor:
% \[
% \sum_{k=1}^K (b_i u_k) \otimes (v_k m_i) = \sum_{k=1}^K u_k \otimes (v_k b_i m_i).
% \]
% Summing this over all $i$ yields:
% \[
% \sum_{i=1}^n b_i y_i = \sum_{i=1}^n \sum_{k=1}^K u_k \otimes (v_k b_i m_i) = \sum_{k=1}^K u_k \otimes \Big( v_k \sum_{i=1}^n b_i m_i \Big).
% \]
% By our initial assumption, $\sum_{i=1}^n b_i m_i = 0$ in $M$. Therefore:
% \begin{equation} \label{eq:tensor_rel}
% \sum_{i=1}^n \sum_{k=1}^K (b_i u_k) \otimes (v_k m_i) = 0 \quad \text{in } B \otimes_A M.
% \end{equation}

% \medskip\noindent
% \textbf{Step 3: Utilizing the $A$-flatness of $M$.} \\
% We now leverage a standard element-theoretic property of flat modules: because $M$ is flat over $A$, any relation of the form $\sum e_l \otimes x_l = 0$ in $E \otimes_A M$ (for any $A$-module $E$) implies there exist $x'_s \in M$ and $a_{ls} \in A$ such that $x_l = \sum_s a_{ls} x'_s$ and $\sum_l e_l a_{ls} = 0$.

% Applying this principle to equation (\ref{eq:tensor_rel}) with $E = B$, where the terms are indexed by pairs $(i, k)$, there exist elements $m'_s \in M$ (for $s = 1, \dots, S$) and scalars $a_{iks} \in A$ such that:
% \begin{align}
% v_k m_i &= \sum_{s=1}^S a_{iks} m'_s \quad \text{in } M \text{ for all } i, k, \label{eq:trivial1} \\
% \sum_{i=1}^n \sum_{k=1}^K (b_i u_k) a_{iks} &= 0 \quad \text{in } B \text{ for all } s. \label{eq:trivial2}
% \end{align}

% \medskip\noindent
% \textbf{Step 4: Reconstructing the $B$-trivialization.} \\
% Consider the evaluation map $\mu_M: B \otimes_A M \to M$ given by $b \otimes m \mapsto bm$. Applying $\mu_M$ to $y_i$ gives:
% \[
% \mu_M(y_i) = \sum_{k=1}^K u_k (v_k m_i) = \Big(\sum_{k=1}^K u_k v_k\Big) m_i = 1 \cdot m_i = m_i.
% \]
% Substitute equation (\ref{eq:trivial1}) into this expansion of $m_i$:
% \[
% m_i = \sum_{k=1}^K u_k \Big( \sum_{s=1}^S a_{iks} m'_s \Big) = \sum_{s=1}^S \Big( \sum_{k=1}^K u_k a_{iks} \Big) m'_s.
% \]
% Define $d_{is} = \sum_{k=1}^K u_k a_{iks} \in B$. This immediately gives our required reconstruction:
% \[
% m_i = \sum_{s=1}^S d_{is} m'_s \quad \text{for all } i = 1, \dots, n.
% \]
% Finally, we must verify that these coefficients annihilate $b_i$. We compute:
% \[
% \sum_{i=1}^n b_i d_{is} = \sum_{i=1}^n b_i \Big( \sum_{k=1}^K u_k a_{iks} \Big) = \sum_{i=1}^n \sum_{k=1}^K (b_i u_k) a_{iks}.
% \]
% By equation (\ref{eq:trivial2}), this sum is exactly $0$ in $B$ for every $s$. 

% Thus, we have successfully trivialized the arbitrary relation $\sum_{i=1}^n b_i m_i = 0$ over $B$. By the equational criterion, $M$ is a flat $B$-module.
% \end{proof}

\begin{lemma}[\stacksproject{092I} (1)]
    \label{lem:weakly-etale-preserves-absolutely-flat}
    Let $A \to B$ be a ring map such that $B \otimes_{A} B \to B$ is flat. If $A$ is an absolutely 
    flat ring, then so is $B$.
    \lean{Ring.AbsolutelyFlat.of_flat_lmul'}
    \leanok
\end{lemma}

\begin{proof}
    \leanok
    \uses{lemma:weakly-etale-flat}
    It follows from \Cref{lemma:weakly-etale-flat} immediately.
\end{proof}

% Note: Gemini give the following nice proof for the localized version.

% \begin{theorem}
% Let $k$ be a field and let $B$ be a local ring over $k$. If the multiplication map $\mu: B \otimes_k B \to B$ makes $B$ a flat module over $B \otimes_k B$, then $B$ is a field.
% \end{theorem}

% \begin{proof}
% Let $A = B \otimes_k B$. The multiplication map $\mu: A \to B$ is a surjective ring homomorphism. Because $B$ is assumed to be a flat $A$-module, $\mu$ is a \emph{flat epimorphism}. A fundamental property of flat epimorphisms is that their kernel, $J = \ker(\mu)$, is a \emph{pure ideal}. The equational criterion for flatness dictates that for any element $z \in J$, there exists a "localizing" element $t \in A$ such that $\mu(t) = 1$ and $t z = 0$.

% Let $\mathfrak{m}$ be the unique maximal ideal of the local ring $B$. We wish to show that $\mathfrak{m} = 0$. Suppose for the sake of contradiction that there exists a non-zero element $x \in \mathfrak{m}$.

% Consider the element $z = x \otimes 1 - 1 \otimes x \in A$. Clearly, $\mu(z) = x - x = 0$, so $z \in J$. By the pureness of $J$, there exists $t \in B \otimes_k B$ such that $\mu(t) = 1$ and 
% \[
% t(x \otimes 1 - 1 \otimes x) = 0 \quad \text{in } B \otimes_k B.
% \]

% Let $K = B/\mathfrak{m}$ be the residue field of $B$, and let $\pi: B \to K$ be the natural quotient map. We base-change our equation along the homomorphism $1 \otimes \pi: B \otimes_k B \to B \otimes_k K$. Because $x \in \mathfrak{m}$, we have $\pi(x) = 0$, which means $(1 \otimes \pi)(1 \otimes x) = 1 \otimes 0 = 0$. 

% Let $\bar{t} = (1 \otimes \pi)(t) \in B \otimes_k K$. Applying $1 \otimes \pi$ to our annihilator equation isolates the $x \otimes 1$ term:
% \[
% \bar{t} \cdot (x \otimes 1) = 0 \quad \text{in } B \otimes_k K.
% \]

% Since $K$ is a field extension of $k$, it is a free $k$-module. Because tensor products preserve freeness, $N = B \otimes_k K$ is a free left $B$-module. The element $x \otimes 1$ represents scalar multiplication by $x$ on $N$. Thus, the relation $x \bar{t} = 0$ implies that $x$ annihilates the \emph{content ideal} $c(\bar{t})$ of $\bar{t}$ in $B$ (the ideal generated by the coordinates of $\bar{t}$ with respect to a basis), meaning $x \cdot c(\bar{t}) = 0$.

% Now, consider the evaluation map $\mu_K: B \otimes_k K \to K$ given by $b \otimes v \mapsto \pi(b)v$. This evaluates $\bar{t}$ at the central point of the local ring:
% \[
% \mu_K(\bar{t}) = \mu_K\big((1 \otimes \pi)(t)\big) = \pi(\mu(t)) = \pi(1) = 1.
% \]
% Since $\mu_K(\bar{t}) = 1 \neq 0$, the coordinates of $\bar{t}$ cannot all map to zero under $\pi$. Thus, they cannot all lie in $\mathfrak{m}$. This implies the content ideal $c(\bar{t})$ is not contained in $\mathfrak{m}$. 

% Because $B$ is a local ring, the only ideal not contained in the unique maximal ideal is the unit ideal itself. Therefore, $c(\bar{t}) = B$.

% Substituting this into our annihilator relation yields $x \cdot B = 0$, which forces $x = 0$. This directly contradicts our initial assumption that $x \neq 0$. We conclude that $\mathfrak{m} = 0$, meaning the local ring $B$ has only the trivial maximal ideal. Therefore, $B$ is a field.
% \end{proof}

% \begin{lemma}[\stacksproject{092I} (2)]
%     \label{lem:weakly-etale-preserves-reduced}
%     Let $A \to B$ be a weakly \'etale ring map. If $A$ is reduced, then $B$ is reduced.
% \end{lemma}

% \begin{proof}
%     TBA.
% \end{proof}

\begin{lemma}[\stacksproject{0905}]
    Let $X$ be a spectral space in which every quasi-compact open
    subset is closed. Then $X$ is profinite.
    \label{lemma:spectral-profinite}
\end{lemma}

\begin{proof}
    It suffices to show that $X$ is Hausdorff and totally disconnected.
    Let $x \neq y$ be in $X$. Since $X$ is quasi-sober and pre-spectral, we may assume
    that there exists a quasi-compact open $U$ with $x \in U$ and $y \not\in U$.
    By assumption, its complement is open and $X$ is Hausdorff. This
    argument also shows that $x$ and $y$ lie in distinct connected components, so
    $X$ is totally disconnected.
\end{proof}

\begin{lemma}[\stacksproject{092F} (2) => (3) (4)]
    %\label{lem:local-ring-is-field-of-absolutely-flat}
    \label{lem:reduced-prime-maximal-of-absolutely-flat}
    If $A$ is an absolutely flat ring, then $A$ is reduced and every prime is maximal.
\end{lemma}

\begin{proof}
    It suffices to show that for every $f \in A$, there exists an idempotent element $e \in A$ such that
    $(f) = (e)$. Indeed, if $f ^ n = 0$ for some $n$, then $e = e ^ n \in (f ^ n) = 0$. Hence $f = 0$.
    For the second claim observe that every quasi-compact open $D(f) = D(e)$ is closed. Hence the claim
    follows from \ref{lemma:spectral-profinite} and the fact that
    every quasi-compact open of $\mathrm{Spec}(A)$ is a finite union of basic opens.

    Now let $f \in A$ be any element. Since $(f)$ is pure by assumption it is nilpotent
    by \verb`Ideal.isIdempotentElem_of_pure` and every idempotent finitely generated ideal
    is generated by an idempotent element by \verb`Ideal.isIdempotentElem_iff_of_fg`.
\end{proof}

\begin{lemma}
    If $A$ is reduced and every prime is maximal, then every local ring of $A$ is a field.
    \label{lemma:reduced-prime-maximal-field}
\end{lemma}

\begin{proof}
    Localizations of reduced rings are reduced and reduced, local rings of Krull dimension $\le 0$
    are fields.
\end{proof}

\section{Weak dimension}

Currently, mathlib does not have $\mathrm{Tor}$ so we give a non-standard, but equivalent definition which
suffices for our purposes.

\begin{definition}
    Let $A$ be a ring. We say it is of \emph{weak dimension} $\le 1$ if every finitely generated ideal of
    $A$ is flat over $A$.
    \label{def:weak-dim-le-one}
    \lean{Ring.WeakDimensionLEOne}
    \leanok
\end{definition}

\begin{theorem}[Lazard]
    Let $M$ be a flat $R$-module. Then $M$ is the directed colimit of free, finite $R$-modules.
    \label{theorem:lazard}
\end{theorem}

\begin{proof}
    \stacksproject{058G}
\end{proof}

\begin{lemma}[\stacksproject{092S}, (1) => (2)]
    If $A$ is of weak-dimension $\le 1$, then every ideal $I \subseteq A$ is flat.
    \uses{def:weak-dim-le-one}
    \label{lemma:weak-dim-ideal-flat}
\end{lemma}

\begin{proof}
    Use the fact that a filtered colimit of flat modules is flat and that
    any ideal is the filtered colimit of its finitely generated subideals.
\end{proof}

\begin{lemma}
    Let $M$ be an $R$-module and $0 = M_0 \subseteq M_1 \subseteq M_n = M$ a
    sequence of submodules. If $M_{j + 1} / M_j$ is flat for all $j$, then
    $M$ is flat.
    \label{lemma:flat-filtration}
\end{lemma}

\begin{proof}
    Inductively apply that extensions of flat modules are flat.
\end{proof}

\begin{lemma}[\stacksproject{092S}, (2) => (4)]
    Let $A$ be a ring of weak dimension $\le 1$ and $M$ a flat $A$-module. Then
    any submodule of $M$ is flat.
    \label{lemma:weak-dim-flat-submodule}
    \lean{Ring.WeakDimensionLEOne.flat_submodule}
    \leanok
    \uses{def:weak-dim-le-one}
\end{lemma}

% There is a much better proof that avoids Lazard, but uses Tor instead.
\begin{proof}
    \uses{theorem:lazard, lemma:flat-filtration, lemma:weak-dim-ideal-flat}
    By \Cref{theorem:lazard} we may write $M = \colim_i M_i$ for finite and free $A$-modules $M_i$.
    Denote by $N_i$ the preimage of $M_i$ in $N$. Then $N = \colim_i N_i$ and
    since the filtered colimit of flat modules is flat, we reduce to the case where $M = R^{\oplus n}$.
    By applying \Cref{lemma:flat-filtration} to the sequence $N_j = N \cap R^{\oplus j}$, it remains
    to show that $N_{j+1} / N_j$ is flat. For this consider
    the projection on the $j + 1$-th factor $N_{j+1} \to R$. Its image is an ideal $I \subseteq R$
    and its kernel is $N_j$. Hence $N_{j + 1} / N_j \cong I$ and $I$ is flat by
    \Cref{lemma:weak-dim-ideal-flat}.
\end{proof}

\begin{lemma}[\stacksproject{092E}]
    Let $A$ be of weak dimension $\le 1$ and $B$ a weakly étale $A$-algebra. Then
    $B$ is of weak dimension $\le 1$.
    \label{lemma:weakly-etale-preserve-weak-dim}
    \uses{def:weak-dim-le-one}
\end{lemma}

\begin{proof}
    \uses{lemma:weakly-etale-flat, lemma:weak-dim-flat-submodule}
    Let $M$ be a flat $B$-module and $N \subseteq M$ a submodule. By
    \Cref{lemma:weakly-etale-flat} it suffices to show that $N$ is $A$-flat.
    Since $B$ is $A$-flat, $M$ is also $A$-flat and hence its submodule $N$
    is $A$-flat by \Cref{lemma:weak-dim-flat-submodule}.
\end{proof}

\begin{lemma}
    Let $I$ be a finitely generated ideal of $\prod_{i \in I} A_i$. Then
    $I = \prod_{i \in I} I_i$ where $I_i$ is the image of $A$ in $A_i$.
    \label{lemma:prod-ideal-fg}
\end{lemma}

\begin{proof}
    TBA.
\end{proof}

\begin{lemma}[\stacksproject{092T}]
    Let $(A_i)_{i \in I}$ be a family of valuation rings. Then
    $\prod_{i \in I} A_i$ is of weak dimension $\le 1$.
    \label{lemma:prod-valuation-ring-weak-dim-integrally-closed}
    \uses{def:weak-dim-le-one}
\end{lemma}

\begin{proof}
    \uses{lemma:prod-ideal-fg}
    Let $I \subseteq \prod_{i \in I} A_i$ be a finitely generated ideal. Let $I_i \subseteq A_i$
    be the image of $I$ in $A_i$.
    By \Cref{lemma:prod-ideal-fg}, $I$ is the product of the $I_i$.
    Since each $A_i$ is a valuation ring, there exists $e_i \in A_i$ such
    that $I_i = (e_i)$.

    TBA.
\end{proof}

\begin{lemma}[\stacksproject{092V}]
    Let $A$ be of weak dimension $\le 1$. Let $B$ be a
    flat $A$-algebra such that $A \to B$ is injective and an epimorphism of rings. Then
    $A$ is integrally closed in $B$.
    \label{lemma:weak-dim-integrally-closed}
\end{lemma}

\begin{proof}
    \uses{lemma:weak-dim-flat-submodule}
    Let $x \in B$ be integral over $A$ and $A' = A[x]$. The map $A \to A'$ is injective and finite, so
    to show $A = A'$ it suffices to check that $A \to A'$ is an epimorphism. By
    \Cref{lemma:weak-dim-flat-submodule}, $A'$ is flat over $A$. Hence
    the composition
    \[
        A' \otimes_{A} A' \to B \otimes_{A} B \to B
    \] is injective.
\end{proof}

\begin{lemma}[\stacksproject{092U}]
    Let $A$ be a domain and $L$ an algebraic extension of $\mathrm{Frac}(A)$.
    If $A$ is integrally closed in $L$, then there exists a cartesian diagram
    of rings
    \[
    \begin{tikzcd}
        A \arrow{r} \arrow{d} & L \arrow{d} \\
        S \arrow{r} & T
    \end{tikzcd}
    \] with $S$ of weak dimension $\le 1$ and $S \to T$ a flat, injective epimorphism of rings.
    \label{lemma:integrally-closed-cartesian-weak-dim}
\end{lemma}

\begin{proof}
    \uses{lemma:prod-valuation-ring-weak-dim-integrally-closed}
    TBA.
\end{proof}

\begin{lemma}[\stacksproject{092W}]
    Let $A$ be a domain and $B$ a weakly étale $A$-algebra. Let $L$ be an algebraic extension
    of $\mathrm{Frac}(A)$ and assume that $A$ is integrally closed in $L$.
    Then $B$ is integrally closed
    in $B \otimes_{A} L$.
    \uses{def:weakly-etale-algebra}
    \label{lemma:weakly-etale-integrally-closed}
\end{lemma}

\begin{proof}
    \uses{lemma:weak-dim-integrally-closed, lemma:weakly-etale-preserve-weak-dim,
      lemma:integrally-closed-cartesian-weak-dim}
    % TODO
\end{proof}

\section{Fields}

\begin{lemma}[\stacksproject{092P}]
    \label{lem:flat-tensor-over-field-imples-algebraic}
    Let $L/K$ be an extension of fields. If $L \otimes_K L \to L$is flat, then $L$ is an algebraic 
    separable extension of $K$.
\end{lemma}

\begin{proof}
    TBA.
\end{proof}

\begin{theorem}[\stacksproject{092Q}, (2) => (3) and last part]
    \label{thm:weakly-etale-imples-ind-etale-over-fields}
    Let $K$ be a field. Suppose that $K \to B$ is weakly étale, then
    \begin{enumerate}
        \item every finitely generated $K$-subalgebra of $B$ is étale over K,
        \item $B$ is a filtered colimit of
    étale $K$-algebras, i.e. $B$ is ind-\'etale.
    \end{enumerate}
    \uses{def:weakly-etale-algebra,
    def:ind-etale}
\end{theorem}

\begin{proof}
    \uses{lem:field-absolutely-flat,
    lem:weakly-etale-preserves-absolutely-flat,
    lemma:etale-weakly-etale-algebra,
    lem:reduced-prime-maximal-of-absolutely-flat,
    lemma:reduced-prime-maximal-field,
    lemma:etale-weakly-etale-algebra,
    lem:weakly-etale-comp,
    lem:flat-tensor-over-field-imples-algebraic}
    It suffices to show the first statement.
    A field is absolutely flat ring by \Cref{lem:field-absolutely-flat},
    hence $B$ is a absolutely flat ring by \Cref{lem:weakly-etale-preserves-absolutely-flat}.
    And $B$ is reduced and every local
    ring is a field, by \Cref{lem:reduced-prime-maximal-of-absolutely-flat} and
    \Cref{lemma:reduced-prime-maximal-field}.

    Let $q \subset B$ be a prime. The ring map $B \to B_q$ is weakly étale by
    \Cref{lemma:etale-weakly-etale-algebra}, hence $B_q$ is weakly étale over $K$
    (\Cref{lem:weakly-etale-comp}). Thus $B_q$ is a separable algebraic extension of $K$ by
    \Cref{lem:flat-tensor-over-field-imples-algebraic}.

    Let $K \subset A \subset B$ be a finitely generated $K$-sub algebra. We will show that
    $A$ is étale over $K$ which will finish the proof of the lemma.

    TBA.

    Then every minimal prime
    $p \subset A$ is the image of a prime $q$ of $B$, see Algebra, Lemma 00FK.
    Thus κ(p) as a subfield of Bq=κ(q) is separable algebraic over K. Hence
    every generic point of Spec(A) is closed (Algebra, Lemma 00GA). Thus dim(A)=0. Then
    A is the product of its local rings, e.g., by Algebra, Proposition 00KJ. Moreover, since A is
    reduced, all local rings are equal to their residue fields which are finite separable over K.
    This means that A is étale over K by Algebra, Lemma 00U3 and finishes the proof.
\end{proof}

\section{Local rings}

\begin{lemma}
    \label{lem:ker-tensor-generated-by}
    Let $A$ be a ring, let $f: R \to R',\, g : S \to S'$ be two ring maps of $A$-algebras.
    Then the kernel of $R \otimes_A S \to R' \otimes_A S'$ is generated by $\ker f \otimes_A S$ and
    $R \otimes_A \ker g$.
\end{lemma}

\begin{proof}
    Omitted.
\end{proof}

\begin{lemma}
    \label{lem:local-dim-zero-tensor}
    Let $k$ be a field, $A$ be a local $k$-algebra of dimension zero, i.e. there is a unique 
    prime ideal in $A$. Suppose that the residue field of $A$ is identified with $k$.
    Then $A \otimes_k A$ is a local $k$ algebra of dimension zero.
\end{lemma}

\begin{proof}
    \uses{lem:ker-tensor-generated-by}
    The unique prime ideal of $A$ is the nilradical $N$ of $A$. By 
    \Cref{lem:ker-tensor-generated-by}, the kernel of $A \otimes_k A \to k = A/N$ is generated by 
    $N \otimes_k A$ and $A \otimes_k N$, which are all consisiting of nilpotent elements.
    Thus the nilpotent ideal of $A \otimes_k A$ is also the maximal ideal. This finishes the proof.
\end{proof}

\begin{lemma}
    \label{lem:bij-on-spectrum-of-unique-lying-over-and-residue-field-eq}
    Let $A \to B$ be a ring map. For all $\mathfrak{p} \subset A$,
    there is a unique prime $\mathfrak{q} \subset B$ lying over $\mathfrak{p}$ and 
    $\kappa(\mathfrak{p}) = \kappa(\mathfrak{q})$. Then $B \otimes_A B \to B$ is bijective on 
    spectra.
\end{lemma}

\begin{proof}
    \uses{lem:local-dim-zero-tensor}
    It suffices to show that, for every prime $p$ of $A$, there is exactly one prime ideal $q'$ 
    of $B \otimes_A B$ lying over $p$. To detect this, we may assume $A$ is a field by replacing
    $A$ with $\kappa(\mathfrak{p})$, $B$ with $\kappa(\mathfrak{p}) \otimes_A B$ which is a local 
    ring. Now the goal follows from \Cref{lem:local-dim-zero-tensor}.
\end{proof}

\begin{lemma}
    \label{lem:iso-of-bij-on-spectrum-and-surj-and-flat}
    Let $A \to B$ be a ring map that is bijective on spectra, as well as surjective and flat, then 
    it is an isomorphism.
\end{lemma}

\begin{proof}
    Recall that a \emph{pure} ideal $I$ in $A$ is an ideal such that $A/I$ is flat. 
    (Use \verb|Ideal.Pure|.) In our case, let $I$ be the kernel of the map $A \to B$. 
    Then $I$ is pure and have empty vanishing locus. But we know that pure ideals are determined by
    their vanishing locus (\verb`Ideal.zeroLocus_inj_of_pure`) and zero ideal is also a pure
    ideal having the same vanishing locus with $I$, thus $I = 0$.
\end{proof}

\begin{lemma}[\stacksproject{04VN}]
    \label{lem:ring-epi-tfae}
    Let $A \to B$ be a ring map. The following are equivalent:
    \begin{enumerate}
        \item $A \to B$ is an epimorphism;
        \item the two ring maps $B \to B \otimes_A B$ are equal;
        \item either of the ring maps $B \to B \otimes_A B$ is an isomorphism, and
        \item the ring map $B \otimes_A B \to B$ is an isomorphism.
    \end{enumerate}
\end{lemma}

\begin{proof}
    Omitted. Use \verb`Algebra.IsEpi`.
\end{proof}

\begin{lemma}[\stacksproject{04VU}]
    \label{lem:isom-of-ff-and-mul-isom}
    Let $A \to B$ be a faithfully flat ring epimorphism. Then $A \to B$ is an isomrophism.
\end{lemma}

\begin{proof}
    \uses{lem:ring-epi-tfae}
    By \Cref{em:ring-epi-tfae}, the map $B \to B \otimes_A B$, which is a base change of $A \to B$,
    is isomorphism. So is $A \to B$ by faithfully flatness.
\end{proof}

\begin{lemma}
    \label{lem:isom-of-unique-lying-over-and-residue-field-eq}
    Let $A \to B$ be a local homomorphism of local rings. For all $\mathfrak{p} \subset A$, 
    there is a unique prime $\mathfrak{q} \subset B$ lying over $\mathfrak{p}$ and 
    $\kappa(\mathfrak{p}) = \kappa(\mathfrak{q})$. Then $A \to B$ is an isomorphism.
\end{lemma}

\begin{proof}
    \uses{lem:bij-on-spectrum-of-unique-lying-over-and-residue-field-eq,
    def:weakly-etale-algebra, 
    lem:iso-of-bij-on-spectrum-and-surj-and-flat, 
    lem:isom-of-ff-and-mul-isom}
    To see this, suppose that we are under the above hypothesis. 
    This implies that $\mu : B \otimes_A B \to B$ is bijective on spectra by 
    \Cref{lem:bij-on-spectrum-of-unique-lying-over-and-residue-field-eq},
    as well as surjective and flat (immediately by \Cref{def:weakly-etale-algebra}). 
    Hence it is an isomorphism by \Cref{lem:iso-of-bij-on-spectrum-and-surj-and-flat}. Together with
    the fact that $A \to B$ is a faithfully (by surjectivity on spectrum) flat, we can apply 
    \Cref{lem:isom-of-ff-and-mul-isom} to conclude $A = B$.
\end{proof}

\begin{lemma}
    \label{lem:totally-disconnected-inverse-limit}
    Let $I$ be a directed set. Let $T_i, \, i \in I$ be a series of totally disconnected 
    topological spaces. Then 
    $$T = \varprojlim_{i \in I} T_i $$ is also totally disconnected.
\end{lemma}

\begin{proof}
    Suppose $x, y$ are two distinct points that lives in the same connected component. Then the 
    projection of $x, y$ will be always fall in the same connected components, thus equal. This 
    is a contradiction.
\end{proof}

\begin{lemma}
    \label{lem:idempotent-in-ind-etale-of-primes}
    % It is unclear whether this lemma is in the most general form.
    Let $B$ be a ind-\'etale algebra over some field $K$. If there are 
    two different prime ideals $q_1$ and $q_2$ in $B$, then $B$ has a nontrivial 
    idempotent element $e$ (i.i. $e^2 = e$).
\end{lemma}

\begin{proof}
    \uses{lem:totally-disconnected-inverse-limit}
    Writing $B$ as a filtered colimit $\colim B_i$ of \'etale algebra over $K$. Each $B_i$ is a
    product of separable field extensions of $K$. In particular, the spectrum of $B_i$'s are totally 
    disconnected. By \Cref{lem:totally-disconnected-inverse-limit}, the spectrum of $B$ is again
    totally disconnected. Thus different prime ideals $q_1$ and $q_2$ livs in 
    different connected components. This giving the desire nontrivial idempotent element.
\end{proof}

\begin{lemma}
    \label{lem:idempotent-in-ind-etale-of-field-ext}
    % It is unclear whether this lemma is in the most general form.
    Let $B$ be a ind-\'etale algebra over some field $K$. If there exists 
    a prime ideal $q$ of $B$, such that the residue field of $q$ is not $K$, then
    $\kappa(q) \otimes_A B$ has a nontrivial element.
    \uses{def:ind-etale}
\end{lemma}

\begin{proof}
    Writing $B$ as a filtered colimit $\colim B_i$ of \'etale algebra over $K$. (Each $B_i$ is a
    product of separable field extensions of $K$.) Let $q_i$ be the inverse image of $q$ in $B_i$,
    $\kappa(q_i)$ be the residue field of $q_i$, then $K_i$ is a separable field extensions of $K$.
    Now $\kappa(q) = \colim \kappa(q_i)$ is again a separable extension of $K$. Then 
    $\kappa(q) \otimes_A B = \kappa(q) \otimes_K \kappa(q)$ splits. The conclusion follows.
\end{proof}

\begin{lemma}
    Let $R$ be a Henselian local ring with separably closed residue field and $S$ a weakly étale local
    $R$-algebra with $R \to S$ a local homomorphism.
    Let $\mathfrak{p}$ be a prime ideal of $R$ and $L$ an algebraic field
    extension of $\kappa(\mathfrak{p})$. Then $L \otimes_{R} S$ has no non-trivial idempotents.
    \label{lemma:weakly-etale-over-sh-aux}
\end{lemma}

\begin{proof}
    \uses{lemma:integral-local-algebraic-residue-field, lemma:tensorprod-local-purely-inseparable, lemma:henselian-local-integral-local}
    Let $R'$ be the integral closure of $R / \mathfrak{p}$ in $L$. Since $R \to R / \mathfrak{p} \to R'$
    is integral, $R'$ is local by \Cref{lemma:henselian-local-integral-local}. Moreover,
    the residue field $\kappa(R')$ is an algebraic extension of $\kappa(R)$
    by \Cref{lemma:integral-local-algebraic-residue-field}. Since $\kappa(R)$ is
    separably closed, the extension is purely inseparable. Hence
    $R' \otimes_{R} S$ is local by \Cref{lemma:tensorprod-local-purely-inseparable}. By
    \Cref{lemma:weakly-etale-integrally-closed} and since $R'$ is integrally closed in $L$,
    the tensor product $R' \otimes_{R} S$ is integrally closed in $L \otimes_{R} S$.
    Since $R' \otimes_{R} S$ is local and any idempotent of $L \otimes_{R} S$ is integral over
    $R' \otimes_{R} S$, the latter can not have any non-trivial idemponent elements.
\end{proof}

\begin{theorem}[\stacksproject{097Z} (Olivier).]
    \label{thm:weakly-etale-over-henselian-sep-closed}
    Let $A \to B$ be a local homomorphism of local rings. If $A$ is henselian, the residue field
    of $A$ is separably closed, and $A \to B$ is weakly étale, then $A = B$.
    \uses{def:weakly-etale-algebra}
\end{theorem}

\begin{proof}
    \uses{lem:isom-of-unique-lying-over-and-residue-field-eq,
    lem:weakly-etale-base-change,
    thm:weakly-etale-imples-ind-etale-over-fields,
    lem:idempotent-in-ind-etale-of-primes,
    lem:idempotent-in-ind-etale-of-field-ext,
    lemma:weakly-etale-over-sh-aux}
    It suffices to show that for all $\mathfrak{p} \subset A$ there is a unique prime 
    $\mathfrak{q} \subset B$ lying over $\mathfrak{p}$ and $\kappa(\mathfrak{p}) = 
    \kappa(\mathfrak{q})$ by \Cref{lem:isom-of-unique-lying-over-and-residue-field-eq}
    
    Note that the fibre ring $\kappa(\mathfrak{p}) \otimes_A B$ is weakly etale over 
    $\kappa(\mathfrak{p})$ by \Cref{lem:weakly-etale-base-change}, thus it is a colimit of étale 
    extensions of $\kappa(\mathfrak{p})$ by \Cref{thm:weakly-etale-imples-ind-etale-over-fields}.
    If the conclusion does not hold, at least one of the following cases is true:
    \begin{enumerate}
        \item there exists more than one prime $\mathfrak{q}\_1, \mathfrak{q}\_2$ lying over 
    $\mathfrak{p}$;
        \item if $\kappa(\mathfrak{p}) \neq \kappa(\mathfrak{q})$ for some $\mathfrak{q}$.
    \end{enumerate}
    In the first case, by \Cref{lem:idempotent-in-ind-etale-of-primes}; in the second case, by 
    \Cref{lem:idempotent-in-ind-etale-of-field-ext}, we can always find some $L$ 
    then $L \otimes_A B$ has a nontrivial idempotent for some (separable) 
    algebraic field extension $L/\kappa(\mathfrak{p})$.

    Now the statement follows from \Cref{lemma:weakly-etale-over-sh-aux}.
\end{proof}

\begin{theorem}
    \label{thm:weakly-etale-over-sh}
    Let $A \to B$ be a local homomorphism of local rings. If $A$ is strictly henselian, 
    and $A \to B$ is weakly étale, then $A = B$.
    \uses{def:weakly-etale-algebra, 
    def:strictly-henselian-local-ring}
\end{theorem}

\begin{proof}
    \uses{thm:weakly-etale-over-henselian-sep-closed,
    lem:sh-iff-henselian-and-sep-closed}
    This is simply \Cref{thm:weakly-etale-over-henselian-sep-closed} plus 
    \Cref{lem:sh-iff-henselian-and-sep-closed}.
\end{proof}

\begin{theorem}
    Let $R \to S$ be weakly étale. Then there exists a faithfully flat ind-étale morphism
    $S \to T$ such that the composition $R \to T$ is ind-étale.
    \label{thm:weakly-etale-ind-etale}
\end{theorem}

\begin{proof}
    \uses{thm:weakly-etale-over-sh}
    TBA.
\end{proof}
